Lifespan analysis

### 2023-08-02 stats/gazemodel.Rmd
edit manuscript figures and corresponding saves

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse) # data handling etc.
library(tidyboot) # for bootstrap CIs

@@

```{r load_data}
gaze_data_kids <- readRDS("../data/tango-model-kids.rds")
gaze_data_adults <- readRDS("../data/tango-model-adults.rds") %>% mutate(age_group = 18)
gaze_data <- full_join(gaze_data_kids, gaze_data_adults)
```

```{r sample}
gazemodel_sample_kids <- gaze_data_kids %>% 
  group_by(age_group) %>%
  mutate(female = ifelse(gender == "f", 1, 0)) %>% 
  summarise(
    n_total = n_distinct(subj_id), 
    age_mean = mean(age, na.rm = T) %>% round(2),
    age_sd = sd(age, na.rm = T) %>% round(2),
    age_min = min(age, na.rm = T),
    age_max = max(age, na.rm = T),
    n_females = ceiling(sum(female/15)),
  )

@@

gazemodel_sample_adults <- gaze_data_adults %>% 
  mutate(female = ifelse(gender == "f", 1, 0)) %>% 
  summarise(
    n_total = n_distinct(subj_id), 
    age_mean = mean(age, na.rm = T) %>% round(2),
    age_sd = sd(age, na.rm = T) %>% round(2),
    age_min = min(age, na.rm = T),
    age_max = max(age, na.rm = T),
    n_females = ceiling(sum(female/15)),
  ) %>% 
  mutate(age_group = 18)

@@

```{r plot}
dev_plot <- gaze_data_kids %>% 
  group_by(subj_id, age, age_group) %>%
  summarise(mean = mean(click_dist_balloons, na.rm = TRUE)) %>% 
  ggplot(., aes(x = age, y = mean)) +
  geom_point(color = "darkgrey", alpha = 0.5) +
  geom_smooth(method = "lm", size = 1, se = T, color = "#006c66", fill = "#006c66") + 
  scale_x_continuous(limits = c(3, 5), breaks = seq(3, 5, 0.5)) +
  scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 1)) +
  labs(x = "Age in years", y = "Average imprecision in target widths")

dev_plot

# ggsave("../figures/dev_plot.png", width = 8, height = 4, scale = 1.2)
```

```{r gazefunnel}
target_position_imprecision <- gaze_data %>%
  group_by(age_group, target_position) %>%
  tidyboot_mean(column = click_dist_balloons, na.rm = TRUE)

target_position_imprecision_ind <- gaze_data %>%
  group_by(subj_id, age_group, target_position) %>%
  summarize(mean = mean(click_dist_balloons, na.rm = TRUE))

@@

ggsave("../figures/gazefunnel.png", width = 6, height = 4, scale = 1.2)
saveRDS(gazefunnel, "../saves/gazefunnel.rds")
```

>>>>

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse) # data handling etc.
library(tidyboot) # for bootstrap CIs
library(coda) # HPDinterval
library(ggpubr) # stat_cor
library(ggdist) # stat_pointinterval
library(matrixStats) # logSumExp
library(ggridges) # for geom_density_ridges
library(ggthemes) # themes for plotting
library(cowplot) # ggdraw, draw_image, plot_grid

@@

```{r functions}
estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}

hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}

hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
```

```{r load_data}
tango_kids <- readRDS("../data/tango-model-kids.rds")
tango_adults <- readRDS("../data/tango-model-adults.rds") %>% mutate(age_group = 18)
tango <- full_join(tango_kids, tango_adults)

# careful, this takes a while... 
model_kids <- readRDS("../data/gazemodel_kids.rds")
model_kids_dev_prior <- readRDS("../data/gazemodel_kids_dev_prior.rds")
```

```{r sample}
gazemodel_sample_kids <- tango_kids %>% 
  group_by(age_group) %>%
  mutate(female = ifelse(gender == "f", 1, 0)) %>% 
  summarise(
    n_total = n_distinct(subj_id), 
    age_mean = mean(age, na.rm = T) %>% round(2),
    age_sd = sd(age, na.rm = T) %>% round(2),
    age_min = min(age, na.rm = T),
    age_max = max(age, na.rm = T),
    n_females = ceiling(sum(female/15)),
  )

@@

gazemodel_sample_adults <- tango_adults %>% 
  mutate(female = ifelse(gender == "f", 1, 0)) %>% 
  summarise(
    n_total = n_distinct(subj_id), 
    age_mean = mean(age, na.rm = T) %>% round(2),
    age_sd = sd(age, na.rm = T) %>% round(2),
    age_min = min(age, na.rm = T),
    age_max = max(age, na.rm = T),
    n_females = ceiling(sum(female/15)),
  ) %>% 
  mutate(age_group = 18)

@@

```{r data_gazefunnel}
target_position_imprecision <- tango %>%
  group_by(age_group, target_position) %>%
  tidyboot_mean(column = click_dist_balloons, na.rm = TRUE)

target_position_imprecision_ind <- tango %>%
  group_by(subj_id, age_group, target_position) %>%
  summarize(mean = mean(click_dist_balloons, na.rm = TRUE))

@@

# saveRDS(gazefunnel, "../saves/gazemodel_funnel.rds")
# ggsave("../figures/gazemodel_funnel.png", width = 6, height = 4, scale = 1.2)
```

# CHILDREN

## Inference

```{r dev_traj_inf}
inf_map_devp <- model_kids_dev_prior %>%
  filter(scope == "global", 
         parameter == "inference", 
         type != "sigma") %>%
  group_by(type) %>%
  summarise(mode = estimate_mode(value)) %>%
  pivot_wider(names_from = "type", values_from = "mode") %>%
  expand_grid(age = seq(0, 3, 0.1)) %>%
  mutate(sd = exp(intercept + slope * age))

inf_samp_devp <- model_kids_dev_prior%>%
  filter(scope == "global", 
         parameter == "inference", 
         type != "sigma") %>%
  pivot_wider(names_from = "type", values_from = "value") %>%
  sample_n(1000) %>%
  expand_grid(age = seq(0, 3, 0.1)) %>%
  mutate(sd = exp(intercept + slope * age))

id_devp <- model_kids_dev_prior%>%
  filter(scope == "id", 
         type == "sd") %>%
  group_by(id) %>%
  summarise(mode = estimate_mode(value),
            lci = hdi_lower(value), 
            uci = hdi_upper(value)) %>%
  left_join(tango_kids %>% 
              select(subj_id, age, age_group) %>% 
              rename(id = subj_id) %>% 
              distinct(id, .keep_all = T)) %>%
  ungroup()

dev_plot <- ggplot() +
  geom_point(data = id_devp, aes(x = age, y = mode), alpha = 0.75, color = "darkgrey") +
  geom_line(data = inf_samp_devp, aes(x = age + 3, y = sd, group = paste(chain,iteration)), col = "blue", alpha = .01) +
  geom_line(data = inf_map_devp, aes(x = age+3, y = sd), col = "black", linewidth = 1.25) +
  scale_x_continuous(limits = c(3, 6), breaks = seq(3, 6, 0.5)) + 
  scale_y_continuous(limits = c(0, 6), breaks = seq(0, 6, 0.25)) +
  coord_cartesian(ylim = c(0, 3)) +
  labs(x = "Age", y = "Inference parameter")

dev_plot
saveRDS(dev_plot, file = "../saves/gazemodel_dev_plot.rds")

# ggsave("../figures/gazemodel_dev.png", width = 8, height = 5, scale = 1, bg = "white")
# ggsave("../figures/gazemodel_dev.pdf", width = 8, height = 5, scale = 1, bg = "white")
```

## Inference parameters individuals

```{r id_inf}
# prepare data
id_inf <- model_kids_dev_prior %>%
  filter(scope == "id", parameter == "inference") %>% 
  group_by(id) %>% 
  mutate(mean = mean(value, na.rm = T))

idinf_plot <- id_inf %>% 
  slice_sample(n = 2000) %>% # for faster debugging
  full_join((tango_kids %>% select(subj_id, age, age_group)), by = join_by(id == subj_id)) %>% 
  ggplot(aes(x = value, y = reorder(id, mean), fill = age)) +
  geom_density_ridges(bandwidth = .05, rel_min_height = .01, size = .25, scale = 3, alpha = .5) + 
  scale_fill_viridis_c(direction = -1, alpha = 0.9, limits = c(3, 6), breaks = seq(3, 6, 0.5)) +
  scale_x_continuous(breaks = seq(0, 7, 0.5)) +
  coord_cartesian(xlim = c(0, 7)) +
  theme(axis.ticks.y = element_blank(), axis.text.y = element_blank()) + 
  labs(x = "Inference parameter", y = "Participants (ordered by mean)", fill = "Age")

idinf_plot
saveRDS(idinf_plot, "../saves/supplements_gazemodel_idinf_plot.rds")

ggsave("../figures/supplements_gazemodel_indinference.png", width = 5, height = 5)
ggsave("../figures/supplements_gazemodel_indinference.pdf", width = 5, height = 5)
```

```{r faceted_inf, message=FALSE, warning=FALSE}
faceted_inf <- model_kids_dev_prior %>%
  filter(scope == "id", parameter == "inference") %>%
  mutate(id = vctrs::vec_group_id(id)) %>% 
  ggplot() + 
  geom_density(aes(x = value, fill = factor(chain)), alpha = .5) +
  stat_pointinterval(aes(x = value)) +
  facet_wrap(~ id, nrow = 6, scales = "free") +
  scale_fill_viridis_d() +
  scale_x_continuous(limits = c(0, 3)) + 
  scale_y_continuous(limits = function(x){c(0, max(0.1, x))}) +
  labs(x = "Inference parameter value", y = "", fill = "Model chains") +
  theme_minimal()

faceted_inf
saveRDS(faceted_inf, "../saves/supplements_gazemodel_facetedinference.rds")

ggsave("../figures/supplements_gazemodel_facetedinference.png", width = 10, height = 6, scale = 1.4, bg = "white")
ggsave("../figures/supplements_gazemodel_facetedinference.pdf", width = 10, height = 6, scale = 1.4, bg = "white")
```

## Recover U pattern

```{r get_click_prior}
get_click_prior <- function(sdTol, eyeCenterLY, eyeCenterLX, eyeCenterRY, eyeCenterRX, targetCenterY, targetCenterX, pupilLX, pupilRX, priorInt, priorSlope, age){

  if(eyeCenterLX > pupilLX) {
    tAlphaL = atan(abs(eyeCenterLX-targetCenterX)/(eyeCenterLY-targetCenterY))
  } else {
    tAlphaL = -atan(abs(eyeCenterLX-targetCenterX)/(eyeCenterLY-targetCenterY))
  }

  #noisyAlphaL = rnorm(1,tAlphaL, sdPer)

  if(eyeCenterRX > pupilRX) {
    tAlphaR = atan(abs(eyeCenterRX-targetCenterX)/(eyeCenterRY-targetCenterY))
  } else {
    tAlphaR = -atan(abs(eyeCenterRX-targetCenterX)/(eyeCenterRY-targetCenterY))
  }

  #noisyAlphaR = rnorm(1,tAlphaR, sdPer)

  bRDist = c()

  bLDist = c()

  for (x in 1:1920){

  if(eyeCenterLX > x) {
    betaL = atan(abs(eyeCenterLX-x)/(eyeCenterLY-targetCenterY))
  } else {
    betaL = -atan(abs(eyeCenterLX-x)/(eyeCenterLY-targetCenterY))
  }
    betaLDist = dnorm(betaL,tAlphaL,sdTol, log = T)

  if(eyeCenterRX > x) {
    betaR = atan(abs(eyeCenterRX-x)/(eyeCenterRY-targetCenterY))
  } else {
    betaR = -atan(abs(eyeCenterRX-x)/(eyeCenterRY-targetCenterY))
  }
    betaRDist = dnorm(betaR,tAlphaR,sdTol, log = T)

    #betaDist = betaLDist + betaRDist

    #bDist[x] <- exp(betaDist)
    bRDist[x] <- betaRDist

    bLDist[x] <- betaLDist

  }

  xRDist = exp(bRDist-logSumExp(bRDist))

  xLDist = exp(bLDist-logSumExp(bLDist))

  priorSD = priorInt + priorSlope * age

  xDist = (xRDist * xLDist) * dnorm(seq(1:1920), mean = 960, sd = priorSD)

  dist = xDist / sum(xDist)

  click = sample(1:1920, prob = xDist, size = 1)-1

  return(click)
}
```

```{r u_pattern}
ind_sd <- model_kids_dev_prior %>%
  filter(scope == "id", type == "sd") %>%
  group_by(id) %>%
  summarise(sdTol = estimate_mode(value)) %>%
  left_join(tango_kids %>% rename(id = subj_id,
                          eyeCenterLY = eye_center_left_y,
                          eyeCenterLX = eye_center_left_x, 
                          eyeCenterRY = eye_center_right_y,
                          eyeCenterRX = eye_center_right_x,
                          pupilLX = pupil_final_left_x,
                          pupilRX = pupil_final_right_x,
                          targetCenterX = target_center_x,
                          targetCenterY = target_center_y) %>%
              mutate(clickDist = abs(click_dist_from_target_center_x)) %>%
              select(id, age, age_group, trial_nr, eyeCenterLX, eyeCenterLY, eyeCenterRX, eyeCenterRY, pupilLX, pupilRX, targetCenterY, targetCenterX, clickDist))

ind_sd_long <- ind_sd %>% slice(rep(1:n(), each = 100))

priorMode <- model_kids_dev_prior %>%
  filter(scope == "global", 
         parameter == "priorSd", 
         type != "sigma") %>%
  group_by(type) %>%
  summarise(mode = estimate_mode(value))

# careful, this runs a while...
gen_model_clicks <- ind_sd_long %>%
  rowwise() %>%
  mutate(modelClick = get_click_prior(
          sdTol = sdTol,
          eyeCenterLY = eyeCenterLY,
          eyeCenterLX = eyeCenterLX, 
          eyeCenterRY = eyeCenterRY,
          eyeCenterRX = eyeCenterRX,
          targetCenterX = targetCenterX,
          pupilLX = pupilLX,
          pupilRX = pupilRX,
          targetCenterY = targetCenterY,
          priorInt = priorMode %>% filter(type == "intercept") %>% pull(mode),
          priorSlope = priorMode %>% filter(type == "slope") %>% pull(mode),
          age = age
          ))

recover_plotdata <- gen_model_clicks %>%
  mutate(
    modelClickDist = abs(modelClick - targetCenterX),
    targetBin = cut(targetCenterX, 
                    breaks=seq(from = 0, to = 1920, by =192),
                    labels=as.character(1:10))
  ) %>%
  group_by(age_group, targetBin) %>%
  summarise(
    data_mean = mean(clickDist), 
    model_mean = mean(modelClickDist)
  )

saveRDS(recover_plotdata, "../saves/gazemodel_recoverU_plotdata.rds")
# recover_plotdata <- readRDS("../saves/gazemodel_recoverU_plotdata.rds")

u_plot <- recover_plotdata %>%
  pivot_longer(cols = c(data_mean, model_mean), names_to = "source", values_to = "imprecision") %>%
  mutate(
    age_group = factor(age_group, levels = c(3, 4, 5), labels = c("3-year-olds", "4-year-olds", "5-year-olds")), 
    imprecision = imprecision / 160,
  ) %>% 
  ggplot(aes(x = targetBin, y = imprecision, col = source)) +
  geom_point(alpha = 0.8) +
  facet_grid(~ age_group) +
  scale_y_continuous(limits = c(0, 5.2), breaks = seq(0, 5, 0.5)) +
  scale_color_manual(values = c("darkgrey", "darkblue"), labels = c("Data", "Model estimate")) +
  labs(x = "Target position", y = "Imprecision in target width", color = "Source") + 
  theme_few() +
  theme(
    legend.position = c(0.84 , 0.8), # c(0,0) bottom left, c(1,1) top-right
    legend.background = element_rect(color = "darkgrey", size = 0.1), 
    legend.text = element_text(size = 8),
    strip.text = element_text(face = "bold", size = 12)
  )

u_plot
saveRDS(u_plot, "../saves/gazemodel_u_plot.rds")
ggsave("../figures/gazemodel_Uplot.png", width = 8, height = 5, scale = 1, bg = "white")
ggsave("../figures/gazemodel_Uplot.pdf", width = 8, height = 5, scale = 1, bg = "white")
```

```{r imprecision_bin_plot}
imprecision_bin_plot <- recover_plotdata %>% 
  mutate(
    model_mean = model_mean / 160, 
    data_mean = data_mean / 160,
  ) %>% 
  ggplot(., aes(x = model_mean, y = data_mean)) +
  geom_point(aes(col = targetBin)) +
  stat_cor(method = "pearson", label.x = 0.2, label.y = 4.9, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") +
  geom_abline(intercept = 0, slope = 1, linetype = 3) +
  scale_color_brewer(palette="BrBG") +
  labs(x = "Model estimated imprecision", y = "Data mean imprecision", color = "Target bin") + 
  scale_x_continuous(limits = c(0, 5.2), breaks = seq(0, 5, 1)) + 
  scale_y_continuous(limits = c(0, 5.2), breaks = seq(0, 5, 1))

saveRDS(imprecision_bin_plot, "../saves/gazemodel_imprecision_bin_plot.rds")
ggsave("../figures/gazemodel_imprecision_bin_plot.png", width = 8, height = 5, scale = 1, bg = "white")
ggsave("../figures/gazemodel_imprecision_bin_plot.pdf", width = 8, height = 5, scale = 1, bg = "white")
```

## Data recovery

```{r model_vs_data}
comparison_model_data_devp <- model_kids_dev_prior %>%
  filter(scope == "id", type == "sd") %>%
  group_by(id) %>%
  summarise(model_mode = estimate_mode(value)) %>%
  left_join(
    tango_kids %>% 
      group_by(subj_id, age, age_group) %>%
      summarise(data_mean = mean(click_dist_balloons)) %>%
      rename(id = subj_id)
  )

model_vs_data_plot <- ggplot(comparison_model_data_devp, aes(x = model_mode, y = data_mean)) +
  geom_point(aes(col = age)) +
  stat_cor(method = "pearson", label.x = 0.05, label.y = 4.9, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") +
  geom_smooth(method = "lm", col = "darkgrey", alpha = 0.25) +
  scale_color_viridis_c(direction = -1, alpha = 0.9, limits = c(3, 6), breaks = seq(3, 6, 0.5)) +
  labs(x = "Model estimated mode", y = "Data imprecision mean", color = "Age") + 
  scale_x_continuous(limits = c(0, 2.1), breaks = seq(0, 2, 0.5)) + 
  scale_y_continuous(limits = c(0, 5), breaks = seq(0, 5, 1))

model_vs_data_plot
saveRDS(model_vs_data_plot, file = "../saves/gazemodel_model_vs_data.rds")
ggsave("../figures/gazemodel_model_vs_data.png", width = 8, height = 5, scale = 1, bg = "white")
ggsave("../figures/gazemodel_model_vs_data.pdf", width = 8, height = 5, scale = 1, bg = "white")
```

# Plot

```{r arrange_plot}
setup_png <- ggdraw() + draw_image("../figures/gazemodel_setup.png")
ulogic_png <- ggdraw() + draw_image("../figures/gazemodel_Ulogic.png")

gazemodel_plot <- ggarrange(
  setup_png,
  dev_plot, 
  NULL, 
  model_vs_data_plot,

  ulogic_png, 
  u_plot, 
  NULL, 
  imprecision_bin_plot,

  ncol = 4, 
  nrow = 2, 
  widths = c(9, 12, 1, 11), 
  labels = c("A", "B", "", "C", "D", "E", "", "F")
)

gazemodel_plot
saveRDS(gazemodel_plot, "../saves/gazemodel_plot.rds")
ggsave("../figures/gazemodel_plot.png", width = 10, height = 5, scale = 1.4, bg = "white")
ggsave("../figures/gazemodel_plot.pdf", width = 10, height = 5, scale = 1.4, bg = "white")
```

### 2023-08-02 stats/lifespan.Rmd
edit manuscript figures and corresponding saves

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse) # data handling etc.
library(tidybayes) # for stat_halfeye, add_predictive_draws
library(tidyboot) # for bootstrapped CIs
library(brms) # modeling
library(cmdstanr) # modeling
library(Rbeast) # Bayesian change point analysis
check_cmdstan_toolchain(fix = TRUE, quiet = TRUE)

@@

@@

## irregular time intervals
ibeast <- beast.irreg(y = y, time = x, season = "none", 
            torder.minmax = c(0, 0), # for constant
            tcp.minmax = c(0, 5), # we assume 3, allow some room for exploration
            tseg.min = 10, 
            mcmc.chains = 4, mcmc.burnin = 1000, mcmc.samples = 10000, 
            ci = TRUE)

@@

```{r plot}
ggplot() +

  geom_jitter(
    data = mdata, 
    aes(x = age, y = mean_imprecision), 
    col = "darkgrey", alpha = 0.75
  ) +

  geom_smooth(
    data = pred, 
    aes(x = age, y = Estimate, ymin = Q2.5, ymax = Q97.5), 
    stat = "identity", size = 1, alpha = 0.15, fill = "#006C66", col = "#006C66",
  ) +

  geom_vline(xintercept = cps$cp, linetype = "dashed", alpha = 0.75, size = 1) +
  # geom_vline(xintercept = cps$lowerCrI, linetype = "dotted", alpha = 0.5, size = 1) +
  # geom_vline(xintercept = cps$upperCrI, linetype = "dotted", alpha = 0.5, size = 1) +

  scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 5)) + 
  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 0.5)) +

  labs(x = "Age in years", y = "Average imprecision in target width")

# ZOOM IN
ggplot() +

  geom_jitter(
    data = mdata, 
    aes(x = age, y = mean_imprecision), 
    col = "darkgrey", alpha = 0.75
  ) +

  geom_smooth(
    data = pred, 
    aes(x = age, y = Estimate, ymin = Q2.5, ymax = Q97.5), 
    stat = "identity", size = 1, alpha = 0.15, fill = "#006C66", col = "#006C66",
  ) +

  geom_vline(xintercept = cps$cp, linetype = "dashed", alpha = 0.75, size = 1) +

  scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 0.5)) + 
  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 0.5)) +

  coord_cartesian(xlim = c(3, 10), ) +

  labs(x = "Age in years", y = "Average imprecision in target width")
```

>>>>

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse) # data handling etc.
library(tidybayes) # for stat_halfeye, add_predictive_draws
library(tidyboot) # for bootstrapped CIs
library(brms) # modeling
library(cmdstanr) # modeling
library(Rbeast) # Bayesian change point analysis
library(janitor) # clean_names
library(ggpubr) # ggarrange

check_cmdstan_toolchain(fix = TRUE, quiet = TRUE)

@@

```{r variation}
lifespan_variation_all <- lifespan_data %>% 
  summarise(
    imprecision_mean = mean(click_dist_balloons, na.rm = T) %>% round(2),
    imprecision_sd = sd(click_dist_balloons, na.rm = T) %>% round(2),
    imprecision_min = min(click_dist_balloons, na.rm = T),
    imprecision_max = max(click_dist_balloons, na.rm = T),
  )

lifespan_variation_agegroups <- lifespan_data %>% 
  group_by(age_group) %>%
  summarise(
    imprecision_mean = mean(click_dist_balloons, na.rm = T) %>% round(2),
    imprecision_sd = sd(click_dist_balloons, na.rm = T) %>% round(2),
    imprecision_min = min(click_dist_balloons, na.rm = T),
    imprecision_max = max(click_dist_balloons, na.rm = T),
  )

lifespan_variation_all
write.csv(lifespan_variation_all, "../saves/lifespan_variation_all.csv", quote = F, row.names = F)
saveRDS(lifespan_variation_all, "../saves/lifespan_variation_all.rds")

lifespan_variation_agegroups
write.csv(lifespan_variation_agegroups, "../saves/lifespan_variation_agegroups.csv", quote = F, row.names = F)
saveRDS(lifespan_variation_agegroups, "../saves/lifespan_variation_agegroups.rds")
```

@@

## irregular time intervals
ibeast <- beast.irreg(y = y, time = x, season = "none", 
            torder.minmax = c(0, 0), # for constant
            # tcp.minmax = c(0, 5), # let the beast decide on its own how many changepoints
            tseg.min = 10, # half of nr data points for decade in adult sample
            mcmc.chains = 4, mcmc.burnin = 1000, mcmc.samples = 10000, 
            ci = TRUE)

@@

```{r plot}
mgaussianprocess <- readRDS("../saves/lifespan_mgaussianprocess.rds")
cps <- readRDS("../saves/lifespan_ibeast_cps.rds")

# https://cran.r-project.org/web/packages/tidybayes/vignettes/tidy-brms.html
lifespan_plot <- mdata %>%
  add_epred_draws(mgaussianprocess, ndraws = 100) %>%
  ggplot(aes(x = age, y = mean_imprecision)) +

  # raw data points
  geom_jitter(data = mdata, aes(x = age, y = mean_imprecision), alpha = 0.5, color = "darkgrey") +

  # model predictions spaghetti lines
  geom_line(aes(y = .epred, group=.draw), alpha = .075, color = "blue") +
  # mean model prediction
  stat_lineribbon(aes(y = .epred), .width = 0, color = "black", fill = "black") +

  # change points from beast
  geom_vline(xintercept = cps$cp, linetype = "dashed", alpha = 0.9, size = 0.75) +

  scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 5)) +
  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 0.5)) + 
  labs(x = "Age in years", y = "Average imprecision in target width")

lifespan_plot

saveRDS(lifespan_plot, "../saves/lifespan_plot.rds")

ggsave("../figures/lifespan_all.png", width = 7, height = 4)
ggsave("../figures/lifespan_all.pdf", width = 7, height = 4)
```

```{r zoomed_plot}
# https://cran.r-project.org/web/packages/tidybayes/vignettes/tidy-brms.html
lifespan_plot_zoom <- mdata %>%
  add_epred_draws(mgaussianprocess, ndraws = 100) %>%
  ggplot(aes(x = age, y = mean_imprecision)) +

  # raw data points
  geom_jitter(data = mdata, aes(x = age, y = mean_imprecision), alpha = 0.5, color = "darkgrey") +

  # model predictions spaghetti lines
  geom_line(aes(y = .epred, group=.draw), alpha = .075, color = "blue") +
  # mean model prediction
  stat_lineribbon(aes(y = .epred), .width = 0, color = "black", fill = "black") +

  # change points from beast
  geom_vline(xintercept = cps$cp, linetype = "dashed", alpha = 0.9, size = 0.75) +

  coord_cartesian(xlim = c(3, 10)) +
  scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 0.5)) +

  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 0.5)) + 
  labs(x = "Age in years", y = "Average imprecision in target width")

lifespan_plot_zoom

saveRDS(lifespan_plot_zoom, "../saves/lifespan_plot_zoom.rds")

# ggsave("../figures/lifespan_zoom.png", width = 7, height = 4)
# ggsave("../figures/lifespan_zoom.pdf", width = 7, height = 4)
```

```{r arrange_plot}
arranged <- ggarrange(
  lifespan_plot, 
  lifespan_plot_zoom, 
  widths = c(2, 1.5), 
  labels = c("A", "B")
)

arranged

ggsave("../figures/lifespan_plot.png", width = 10, height = 3, scale = 1.2)
ggsave("../figures/lifespan_plot.pdf", width = 10, height = 3, scale = 1.2)
```

```{r try_ggbreak}
library(ggbreak)

lifespan_cut <- mdata %>%
  add_epred_draws(mgaussianprocess, ndraws = 100) %>%
  ggplot(aes(x = age, y = mean_imprecision)) +

  # raw data points
  geom_jitter(data = mdata, aes(x = age, y = mean_imprecision), alpha = 0.5, color = "darkgrey") +

  scale_x_cut(breaks = c(18), scales = "free", space = 0.001) +

  # model predictions spaghetti lines
  geom_line(aes(y = .epred, group=.draw), alpha = .075, color = "blue") +
  # mean model prediction
  stat_lineribbon(aes(y = .epred), .width = 0, color = "black", show.legend = F) +

  # change points from beast
  geom_vline(xintercept = cps$cp, linetype = "dashed", alpha = 0.9, size = 0.75) +

  scale_x_continuous(limits = c(3, 80), breaks = c(3:17, 20, 30, 40, 50, 60, 70, 80)) +
  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 0.5)) +

  labs(x = "Age", y = "Mean imprecision", xdist = "", ydist = "")

lifespan_cut
```

```{r try_ggh4x}
library(ggh4x)

mdata %>%
  mutate(my_facet = age > 20.00) %>% 
  add_epred_draws(mgaussianprocess, ndraws = 100) %>%

  ggplot(aes(x = age, y = mean_imprecision)) +

    # raw data points
  geom_jitter(data = mdata, aes(x = age, y = mean_imprecision), alpha = 0.5, color = "darkgrey") +

    # model predictions spaghetti lines
  geom_line(aes(y = .epred, group=.draw), alpha = .075, color = "blue") +
  # mean model prediction
  stat_lineribbon(aes(y = .epred), .width = 0, color = "black", show.legend = F) +

  # for gap in x axis
  facet_grid(~ my_facet, scales = "free_x") +
  theme(strip.text.x = element_blank()) +

  ggh4x::facetted_pos_scales(x = list(
    my_facet == FALSE ~ scale_x_continuous(limits = c(3, 20), breaks = seq(3, 19, 1)),
    my_facet == TRUE ~ scale_x_continuous(limits = c(20, 80), breaks = seq(20, 80, 10))
)) +

  geom_vline(data = data.frame(xint=cps$cp[1:4], my_facet = FALSE), aes(xintercept = xint), linetype = "dotted") +
  geom_vline(data = data.frame(xint=cps$cp[5:6], my_facet = TRUE), aes(xintercept = xint), linetype = "dotted") +

  labs(x = "Age in years", y = "Average imprecision in target width") +

  # get rid of space between facets
  theme(panel.spacing = unit(0.1, "lines"))
```
